Adversarial State Aggregation

### 2019-11-01 minutia/paper/paper.tex
paper updated

\author{%
Shayan Amani \\ %\thanks{Use footnote for providing further information
%    about author (webpage, alternative address)---\emph{not} for acknowledging
%    funding agencies.}%
Department of Computer Science\\
University of New Hampshire \\
\texttt{\{shayan\}\{mpetrik\}@cs.unh.edu} \\
% examples of more authors
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \AND
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
}

@@

    \section{Method}
    For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations
    to the end of this paper. We use model-free LSPI and LSTDQ \citep{Lagoudakis2003} to calculate and
    evaluate the policy of actions, respectively.

>>>>

\author{%
Authors \\ %\thanks{Use footnote for providing further information
%    about author (webpage, alternative address)---\emph{not} for acknowledging
%    funding agencies.}%
Department of Computer Science\\
University of New Hampshire \\
\texttt{\{authors\}@cs.unh.edu} \\
% examples of more authors
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \AND
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
% \And
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email} \\
}

@@

    \section{Method}
    For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations
    to the end of this paper. We use model-free LSPI and LSTDQ \citep{Lagoudakis2003} to update and
    evaluate the policy of actions, respectively. CRAAM, on the other hand, as a exact method tries to
